---
title: "Data cleaning"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Desktop/Machine Learning/Kaggle/Sberbank/sberbank")

```

```{r}
  library(data.table)
  library(readr)
  library(caret)
  library(dplyr)
  library(xgboost)
  library(lubridate)
  library(Matrix)
  library(stringr)

  train <- fread('../input/train.csv')
  test <- fread('../input/test.csv')
  
  train$type = "train"
  test$type = "test"
  
  train <- train %>% mutate(max_floor = as.numeric(max_floor), kitch_sq=as.numeric(kitch_sq), num_room=as.numeric(num_room), material = as.numeric(material), build_year=as.numeric(build_year), state = as.numeric(state))
  
  full <- bind_rows(train,test)
  
basic_features <- c("id", "timestamp", "price_doc", "full_sq", "life_sq", "kitch_sq", "num_room", "floor", "max_floor", "material", "build_year", "state", "product_type", "sub_area")

rest_features <- setdiff(names(train), basic_features)

  train <- train %>% select(one_of(c(basic_features,rest_features)))  
  test <- test %>% select(one_of(setdiff(c(basic_features,rest_features),"price_doc")))
```


## Price Doc
```{r}
train %>% count(price_doc) %>% filter(price_doc <= 3000000) %>% arrange(desc(n))

#potentially remove these rows from train set
train <- train %>% mutate(strange_price = ifelse(price_doc %in% c(990000,999000,1000000,1100000,2000000,3000000), 1,0))

train <- train %>% filter(price_doc <= 1e08)
```

## Full square
```{r}

train <- train %>% mutate(full_sq = ifelse(full_sq > 1000, full_sq/100, full_sq))
train <- train %>% mutate(full_sq = ifelse(full_sq > 100 & product_type=="OwnerOccupier" & num_room <= 2, full_sq/10, full_sq))
train <- train %>% mutate(full_sq = ifelse(full_sq > 300 & product_type=="Investment", full_sq/10, full_sq))

test <- test %>% mutate(full_sq = ifelse(full_sq > 300 & product_type=="OwnerOccupier" & num_room <= 2, full_sq/10, full_sq))

train <- train %>% mutate(strange_full_sq = ifelse(full_sq <= 9, full_sq+1,0), full_sq = ifelse(full_sq <= 9, NA, full_sq))

test <- test %>% mutate(strange_full_sq = ifelse(full_sq <= 9, full_sq+1,0), full_sq = ifelse(full_sq <= 9, NA, full_sq))
```

## Living area 
```{r}

train <- train %>% mutate(life_sq = ifelse(life_sq > 1000, life_sq/100, life_sq))
train <- train %>% mutate(life_sq = ifelse(life_sq/10==full_sq, life_sq/10, life_sq))
train <- train %>% mutate(life_sq = ifelse((full_sq >0 & life_sq/full_sq > 4), life_sq/10, life_sq))

test <- test %>% mutate(life_sq = ifelse(life_sq/10==full_sq, life_sq/10, life_sq))
test <- test %>% mutate(life_sq = ifelse((full_sq >0 & life_sq/full_sq > 4), life_sq/10, life_sq))

### swapped vlaues between life and full_sq
train[train$life_sq>train$full_sq & !(is.na(train$life_sq) | is.na(train$full_sq)),c("full_sq","life_sq")]<- train[train$life_sq>train$full_sq & !(is.na(train$life_sq) | is.na(train$full_sq)),c("life_sq","full_sq")]

test[test$life_sq>test$full_sq & !(is.na(test$life_sq) | is.na(test$full_sq)),c("full_sq","life_sq")]<- test[test$life_sq>test$full_sq & !(is.na(test$life_sq) | is.na(test$full_sq)),c("life_sq","full_sq")]

train <- train %>% mutate(strange_life_sq = ifelse(life_sq < 7, life_sq+1,0), life_sq = ifelse(life_sq <= 1, NA, life_sq))

test <- test %>% mutate(strange_life_sq = ifelse(life_sq <= 1, life_sq+1,0), strange_life_sq= ifelse(is.na(strange_life_sq),0,strange_life_sq), life_sq = ifelse(life_sq <= 1, NA, life_sq))

```



## Kitchen area 
```{r}

## build years in kitch_sq
train <- train %>% mutate(build_year = ifelse(kitch_sq>1900,kitch_sq,build_year))
test <- test %>% mutate(build_year = ifelse(kitch_sq>1900,kitch_sq,build_year))

## sometimes kitch_sq >= full_sq
train <- train %>% mutate(kitch_sq = ifelse(kitch_sq >= full_sq, NA, kitch_sq))
test <- test %>% mutate(kitch_sq = ifelse(kitch_sq >= full_sq, NA, kitch_sq))

### kitch_sq >= life_sq
train <- train %>% mutate(kitch_sq = ifelse(kitch_sq >= life_sq, NA, kitch_sq))
test <- test %>% mutate(kitch_sq = ifelse(kitch_sq >= life_sq, NA, kitch_sq))

train <- train %>% mutate(strange_kitch_sq = ifelse(kitch_sq <= 1, kitch_sq+1,0),kitch_sq = ifelse(kitch_sq <= 1, NA, kitch_sq))
test <- test %>% mutate(strange_kitch_sq = ifelse(kitch_sq <= 1, kitch_sq+1,0),kitch_sq = ifelse(kitch_sq <= 1, NA, kitch_sq))

```



## Number of living rooms
```{r}
train <- train %>% mutate(num_room = ifelse(num_room >= 10 | num_room <= 0, NA, num_room))
test <- test %>% mutate(num_room = ifelse(num_room >= 10 | num_room <= 0, NA, num_room))

```


## build year
```{r}
table(train$build_year)

train <- train %>% mutate(build_year = ifelse(build_year > 1000000, mean(as.numeric(c(str_sub(build_year,1,4),str_sub(build_year,5,8)))), build_year))

train <- train %>% mutate(build_year = ifelse(build_year > 2900, as.numeric(str_c("1",str_sub(build_year,2,4))), build_year))

train <- train %>% mutate(strange_build_year = ifelse(build_year <= 1, build_year+1,0), build_year = ifelse(build_year < 1800, NA, build_year))

test <- test %>% mutate(strange_build_year = ifelse(build_year <= 1, build_year+1,0), build_year = ifelse(build_year < 1800, NA, build_year))


table(train$build_year)
table(test$build_year)
```

## floor
```{r}

train <- train %>% mutate(floor = ifelse(floor > 45, round(floor/10), floor))
test <- test %>% mutate(floor = ifelse(floor > 45, round(floor/10), floor))
table(train$floor)
table(test$floor)

### to do: probably some floors of 1 are not real information
```

## max floor
```{r}

train <- train %>% mutate(max_floor = ifelse(max_floor>100, as.numeric(str_sub(max_floor,2,3)),max_floor))

train <- train %>% mutate(strange_max_floor = ifelse(max_floor <= 1, max_floor+1,0), max_floor = ifelse(max_floor > 60 | max_floor <=0, NA, max_floor))

test <- test %>% mutate(strange_max_floor = ifelse(max_floor <= 1, max_floor+1,0), max_floor = ifelse(max_floor > 60 | max_floor <=0, NA, max_floor))

```


## state
```{r}
train <- train %>% mutate(state= ifelse(state>10, round(state/10),state))

train <- train %>% mutate(state = factor(state, exclude=NULL))
test <- test %>% mutate(state = factor(state, exclude=NULL))

```


## material
```{r}
train <- train %>% mutate(material = ifelse(material == 3, NA, material), material=factor(material, exclude=NULL))
test <- test %>% mutate(material = ifelse(material == 3, NA, material), material=factor(material, exclude=NULL))
```


## product_type
```{r}
str(train$product_type)
train <- train %>% mutate(product_type = factor(product_type, exclude=NULL))
test <- test %>% mutate(product_type = factor(product_type, exclude=NULL))
table(test$product_type)

```

# Subarea
```{r}
train <- train %>% mutate(sub_area = factor(sub_area, exclude=NULL))
test <- test %>% mutate(sub_area = factor(sub_area, exclude=NULL)) # only 145 Poselenie Klenovskoe not in test set
```



# missing values in other features

```{r fig.height=12}
missing_values <- train %>% summarize_each(funs(sum(is.na(.))/n()))

missing_values <- gather(missing_values, key="feature", value="missing_pct")
missing_values %>% 
  ggplot(aes(x=reorder(feature,missing_pct),y=missing_pct)) +
  geom_bar(stat="identity",fill="red")+
  coord_flip()+theme_bw()

missing_values %>% filter(missing_pct>0) %>% arrange(desc(missing_pct))

missing_values <- test %>% summarize_each(funs(sum(is.na(.))/n()))

missing_values <- gather(missing_values, key="feature", value="missing_pct")
missing_values %>% 
  ggplot(aes(x=reorder(feature,missing_pct),y=missing_pct)) +
  geom_bar(stat="identity",fill="red")+
  coord_flip()+theme_bw()

missing_values %>% filter(missing_pct>0) %>% arrange(desc(missing_pct))

```


# area_m ok

#### Note: use raion popul, seems more reliable


```{r}
train <- train %>% mutate(school_education_centers_raion_pct = school_education_centers_raion/area_m*1e+06)
test <- test %>% mutate(school_education_centers_raion_pct = school_education_centers_raion/area_m*1e+06)

train <- train %>% mutate(school_education_centers_top_20_raion = ifelse(school_education_centers_top_20_raion>=1,1,0))
test <- test %>% mutate(school_education_centers_top_20_raion = ifelse(school_education_centers_top_20_raion>=1,1,0))

train <- train %>% mutate(hospital_beds_raion_pct = hospital_beds_raion/raion_popul)
test <- test %>% mutate(hospital_beds_raion_pct = hospital_beds_raion/raion_popul)

train <- train %>% mutate(healthcare_centers_raion_pct = healthcare_centers_raion/area_m*1e+06)
test <- test %>% mutate(healthcare_centers_raion_pct = healthcare_centers_raion/area_m*1e+06)

train <- train %>% mutate(university_top_20_raion = ifelse(university_top_20_raion>=1,1,0))
test <- test %>% mutate(university_top_20_raion = ifelse(university_top_20_raion>=1,1,0))

train <- train %>% mutate(sport_objects_raion_pct = sport_objects_raion/area_m*1e+06)
test <- test %>% mutate(sport_objects_raion_pct = sport_objects_raion/area_m*1e+06)

train <- train %>% mutate(additional_education_raion_pct = additional_education_raion/area_m*1e+06)
test <- test %>% mutate(additional_education_raion_pct = additional_education_raion/area_m*1e+06)

train <- train %>% mutate(culture_objects_top_25 = NULL, culture_objects_top_25_raion = ifelse(culture_objects_top_25_raion >=2, 2, ifelse(culture_objects_top_25_raion>=1,1,0)))
test <- test %>% mutate(culture_objects_top_25 = NULL, culture_objects_top_25_raion = ifelse(culture_objects_top_25_raion >=2, 2, ifelse(culture_objects_top_25_raion>=1,1,0)))

train <- train %>% mutate(shopping_centers_raion_pct = shopping_centers_raion/area_m*1e+06)
test <- test %>% mutate(shopping_centers_raion_pct = shopping_centers_raion/area_m*1e+06)

train <- train %>% mutate(office_raion = office_raion/area_m*1e+06)
test <- test %>% mutate(office_raion = office_raion/area_m*1e+06)

train <- train %>% mutate(thermal_power_plant_raion = as.numeric(as.factor(thermal_power_plant_raion)))
test <- test %>% mutate(thermal_power_plant_raion = as.numeric(as.factor(thermal_power_plant_raion)))

train <- train %>% mutate(incineration_raion = as.numeric(as.factor(incineration_raion)))
test <- test %>% mutate(incineration_raion = as.numeric(as.factor(incineration_raion)))

train <- train %>% mutate(oil_chemistry_raion = as.numeric(as.factor(oil_chemistry_raion)))
test <- test %>% mutate(oil_chemistry_raion = as.numeric(as.factor(oil_chemistry_raion)))

train <- train %>% mutate(radiation_raion = as.numeric(as.factor(radiation_raion)))
test <- test %>% mutate(radiation_raion = as.numeric(as.factor(radiation_raion)))

train <- train %>% mutate(railroad_terminal_raion = as.numeric(as.factor(railroad_terminal_raion)))
test <- test %>% mutate(railroad_terminal_raion = as.numeric(as.factor(railroad_terminal_raion)))

train <- train %>% mutate(big_market_raion = as.numeric(as.factor(big_market_raion)))
test <- test %>% mutate(big_market_raion = as.numeric(as.factor(big_market_raion)))

train <- train %>% mutate(nuclear_reactor_raion = as.numeric(as.factor(nuclear_reactor_raion)))
test <- test %>% mutate(nuclear_reactor_raion = as.numeric(as.factor(nuclear_reactor_raion)))

train <- train %>% mutate(detention_facility_raion = as.numeric(as.factor(detention_facility_raion)))
test <- test %>% mutate(detention_facility_raion = as.numeric(as.factor(detention_facility_raion)))
```





### Deal with NaNs

#### impute product_type with mice package


#### replace missing life_sq according to full_sq square mean ratio
```{r}
train <- train %>% mutate(life_sq=ifelse(is.na(life_sq) & !is.na(full_sq), full_sq*0.64, life_sq))
test <- test %>% mutate(life_sq=ifelse(is.na(life_sq) & !is.na(full_sq), full_sq*0.64, life_sq))
```

### replace num_floor NA

### take the appartment_id to fill in nan


# Feature engineering
```{r}
# floor by max_floor
train <- train %>% mutate(floor_by_maxfloor = floor/max_floor, floor_by_maxfloor=ifelse(floor_by_maxfloor>1,NA,floor_by_maxfloor))
test <- test %>% mutate(floor_by_maxfloor = floor/max_floor, floor_by_maxfloor=ifelse(floor_by_maxfloor>1,NA,floor_by_maxfloor))

# average room size
train <- train %>% mutate(roomsize = (life_sq-kitch_sq)/num_room, roomsize=ifelse(roomsize<=0 | roomsize > 200, NA,roomsize)) 
test <- test %>% mutate(roomsize = (life_sq-kitch_sq)/num_room, roomsize=ifelse(roomsize<=0 | roomsize > 200, NA,roomsize))

# relative proportion of area for life kitchen
train <- train %>% mutate(life_proportion = life_sq/full_sq)
test <- test %>% mutate(life_proportion = life_sq/full_sq)

train <- train %>% mutate(kitchen_proportion = kitch_sq/full_sq)
test <- test %>% mutate(kitchen_proportion = kitch_sq/full_sq)


# age when sold
train <- train %>% mutate(age = -interval(timestamp, make_date(year=build_year)) / years(1))
test <- test %>% mutate(age = -interval(timestamp, make_date(year=build_year)) / years(1))

# year 
train <- train %>% mutate(year = year(timestamp))
test <- test %>% mutate(year = year(timestamp))

# year_month
train <- train %>% mutate(year_month = make_date(year(timestamp),month(timestamp)))
test <- test %>% mutate(year_month = make_date(year(timestamp),month(timestamp)))

# day of week
train <- train %>% mutate(day_of_week = wday(train$timestamp))
test <- test %>% mutate(day_of_week = wday(test$timestamp))

# day of month
train <- train %>% mutate(day_of_month = mday(train$timestamp))
test <- test %>% mutate(day_of_month = mday(test$timestamp))


# month of year
train <- train %>% mutate(month_of_year = month(train$timestamp))
test <- test %>% mutate(day_of_week = month(test$timestamp))

# week of year
train <- train %>% mutate(week_of_year = week(train$timestamp))
test <- test %>% mutate(week_of_year = week(test$timestamp))


# sales per month
train <- train %>% group_by(year_month) %>% summarize(n_sales = n()) %>% left_join(train,by="year_month")
test <- test %>% group_by(year_month) %>% summarize(n_sales = n()) %>% left_join(test,by="year_month")

# okrugs
okrugs <- read_csv('./input/okrugs.csv')
names(okrugs)[1]<-"sub_area"
train <- train %>% left_join(okrugs,by="sub_area")
test <- test %>% left_join(okrugs,by="sub_area")

# average price by raion
train <- train %>% group_by(sub_area) %>% summarize(mean_price_raion = mean(price_doc)) %>% right_join(train,by="sub_area")
test <- train %>% group_by(sub_area) %>% summarize(mean_price_raion = mean(price_doc)) %>% right_join(test,by="sub_area")

# average price per sqm per raion



# average price by raion per year
train <- train %>% group_by(sub_area, year) %>% summarize(mean_price_raion_year = mean(price_doc)) %>% right_join(train,by="sub_area")
test <- train %>% group_by(sub_area, year) %>% summarize(mean_price_raion_year = mean(price_doc)) %>% right_join(test,by="sub_area")

# population density per raion
train <- train %>% mutate(pop_density_raion = raion_popul/area_m)
test <- test %>% mutate(pop_density_raion = raion_popul/area_m)

# average building hight per raion (to do - full dataset)
train <- train %>% group_by(sub_area) %>% summarize(mean_building_height = mean(max_floor,na.rm=T)) %>% left_join(train,by="sub_area")

# longitude latitude of raions (to do)

# number of missing values per row (to do)

# num of floor from top 
train <- train %>% mutate(floor_from_top = max_floor - floor)
test <- test %>% mutate(floor_from_top = max_floor - floor)

# extra area
train <- train %>% mutate(extra_floor = full_sq - life_sq)
test <- test %>% mutate(extra_floor = full_sq - life_sq)

# average distance to important things


####
train_df["ratio_preschool"] = train_df["children_preschool"] / train_df["preschool_quota"].astype("float")
test_df["ratio_preschool"] = test_df["children_preschool"] / test_df["preschool_quota"].astype("float")

train_df["ratio_school"] = train_df["children_school"] / train_df["school_quota"].astype("float")
test_df["ratio_school"] = test_df["children_school"] / test_df["school_quota"].astype("float")

```


# model fit
```{r}
rowsstd <- train[which(!(train$price_doc %in% c(1000000,2000000))),]
rows100 <- sample_frac(train[train$price_doc == 1000000,],0.0149584)
rows200 <- sample_frac(train[train$price_doc == 2000000,],0.081556)

train0 <- rbind(rowsstd,rows100,rows200)
outcomes0 <- train0$price_doc
train0 <- select(train0, -price_doc, -strange_price_doc, -timestamp, -year_month, -year)

train1 <- train %>% filter(product_type == "OwnerOccupier")
test1 <- test %>% filter(product_type == "OwnerOccupier")
outcomes1 <- train1$price_doc

train1 <- select(train1, -price_doc, -strange_price_doc, -timestamp, -year_month, -year)

train2 <- train %>% filter(product_type == "Investment")
test2 <- test %>% filter(product_type == "Investment")
outcomes2 <- train2$price_doc

train2 <- select(train2, -price_doc, -strange_price_doc, -timestamp, -year_month, -year)


dummy <- dummyVars(~.,train0)
train_matrix0 <- predict(dummy,train0)
test_matrix0 <- predict(dummy,test)

train_sparse0 <- Matrix(train_matrix0,sparse = T)
test_sparse0 <- Matrix(test_matrix0,sparse = T)
dtrain0 <- xgb.DMatrix(data = train_sparse0,label=log(outcomes0))
dtest0<- xgb.DMatrix(data=test_sparse0)

dummy <- dummyVars(~.,train1)
train_matrix1 <- predict(dummy,train1)
test_matrix1 <- predict(dummy,test1)

train_sparse1 <- Matrix(train_matrix1,sparse = T)
test_sparse1 <- Matrix(test_matrix1,sparse = T)
dtrain1 <- xgb.DMatrix(data = train_sparse1,label=log(outcomes1))
dtest1 <- xgb.DMatrix(data=test_sparse1)

dummy <- dummyVars(~.,train2)
train_matrix2 <- predict(dummy,train2)
test_matrix2 <- predict(dummy,test2)

train_sparse2 <- Matrix(train_matrix2,sparse = T)
test_sparse2 <- Matrix(test_matrix2,sparse = T)
dtrain2 <- xgb.DMatrix(data = train_sparse2,label=log(outcomes2))
dtest2 <- xgb.DMatrix(data=test_sparse2)

# Params for xgboost
param <- list(objective="reg:linear",
              eval_metric = "rmse",
              eta = .05,
              gamma = 1,
              max_depth = 4,
              min_child_weight = 1,
              subsample = .7,
              colsample_bytree = .7
)

#Cross validation - determine CV scores & optimal amount of rounds
cat("XGB cross validation")
xgb_cv <- xgb.cv(data = dtrain,
                nfold = 5,
                params = param,
                nrounds = 150000,
                maximize = FALSE,
                prediction = TRUE,
                print.every.n = 5,
                early.stop.round = 100
);gc()
rounds <- xgb_cv$best_iteration


#Cross validation - determine CV scores & optimal amount of rounds
cat("XGB cross validation")
xgb_cv <- xgb.cv(data = dtrain1,
                nfold = 5,
                params = param,
                nrounds = 150000,
                maximize = FALSE,
                prediction = TRUE,
                print.every.n = 5,
                early.stop.round = 100
);gc()
rounds1 <- xgb_cv$best_iteration

#Cross validation - determine CV scores & optimal amount of rounds
cat("XGB cross validation")
xgb_cv <- xgb.cv(data = dtrain2,
                nfold = 5,
                params = param,
                nrounds = 150000,
                maximize = FALSE,
                prediction = TRUE,
                print.every.n = 5,
                early.stop.round = 100
);gc()
rounds2 <- xgb_cv$best_iteration

# Train model
cat("XGB training")
xgb_model0 <- xgb.train(data = dtrain0,
                       params = param,
                       watchlist = list(train = dtrain),
                       nrounds = rounds,
                       verbose = 1,
                       print.every.n = 5
);gc()

# Train model
cat("XGB training")
xgb_model1 <- xgb.train(data = dtrain1,
                       params = param,
                       watchlist = list(train = dtrain1),
                       nrounds = rounds1,
                       verbose = 1,
                       print.every.n = 5
);gc()

# Train model
cat("XGB training")
xgb_model2 <- xgb.train(data = dtrain2,
                       params = param,
                       watchlist = list(train = dtrain2),
                       nrounds = rounds2,
                       verbose = 1,
                       print.every.n = 5
);gc()

# Feature importance
cat("Plotting feature importance")
names <- dimnames(train_sparse)[[2]]
importance_matrix <- xgb.importance(names,model=xgb_model)
xgb.plot.importance(importance_matrix[1:50,])

# Predict and output csv
cat("Predictions")
preds0 <- predict(xgb_model0,dtest0)
preds0 <- exp(preds0)

preds1 <- predict(xgb_model1,dtest1)
preds1 <- exp(preds1)

preds2 <- predict(xgb_model2,dtest2)
preds2 <- exp(preds2)

preds <- data.frame(id=test$id,pred=NA)


preds$pred[which(is.na(test$product_type))] <- preds0[which(is.na(test$product_type))]

preds$pred[which(test$id %in% test1$id)] <- preds1
preds$pred[which(test$id %in% test2$id)] <- preds2


write.table(data.frame(id=test_ids, price_doc=preds$pred), "submission.csv", sep=",", dec=".", quote=FALSE, row.names=FALSE)

```




## Problem 1: wrong scale nivau

## Area measures 0 and 1 seem to not make sense


## Problem 1: Outliers for Area (full and live)
## Problem 2: build year has strange values
## Problem 3: sometimes max_floor > floor

## some values in kitch_sq are years possibly build_year
