---
title: "A Collection of New Features"
author: "Philipp Spachtholz"
output:
  html_document:
    fig_height: 4
    fig_width: 7
    theme: paper
---

There are already a lot of good ideas for feature engineering around for this competition. However, they are all scattered across
different kernels and discussion threads.**Therefore, my plan here is to provide an easily accessible and extensible list of ideas for feature engineering (together with their implementation in R).**

```
Recent updates:
- grouped appartments in the same building complex together
```

Feel free to add new ideas in the comments and
I'll add them to the list and please don't forget to **upvote** if you find it useful :-).

Having said all that, let's jump right into it:

### Initialization
```{r message=FALSE, warning=FALSE}
  library(data.table)
  library(dplyr)
  library(lubridate)
  library(stringr)

  train <- fread('../input/train.csv')
  
```

##### Minimal data cleaning

```{r }
train <- train %>% 
  mutate(max_floor = as.numeric(max_floor), kitch_sq=as.numeric(kitch_sq), num_room=as.numeric(num_room), build_year=as.numeric(build_year), sub_area=as.factor(sub_area))
train <- train %>% 
  filter(build_year < 2020)

```


### Time features

#### Split the timestamp feature

```{r }
  # year
  train <- train %>% 
    mutate(year = year(timestamp))

  # year_month
  train <- train %>% 
    mutate(year_month = make_date(year(timestamp),month(timestamp)))
```


#### Get month, week, weekday

```{r }
  # month of year
  train <- train %>% 
    mutate(month_of_year = month(train$timestamp))

  # week of year
  train <- train %>% 
    mutate(week_of_year = week(train$timestamp))

  # day of month
  train <- train %>% 
    mutate(day_of_month = mday(train$timestamp))
  
  # weekday
  train <- train %>% 
    mutate(day_of_week = wday(train$timestamp))

```


### House characteristics


```{r }
  # number of floors to the top of house
  train <- train %>% 
    mutate(floor_from_top = max_floor - floor)
  
  # relative position of floor in house
  train <- train %>% 
    mutate(floor_by_maxfloor = floor/max_floor)
  
  # average room size
  train <- train %>% 
    mutate(roomsize = (life_sq-kitch_sq)/num_room) 
  
  # relative proportion of living area
  train <- train %>% 
    mutate(life_proportion = life_sq/full_sq)
  
  # relative proportion of kitchen area
  train <- train %>% 
    mutate(kitchen_proportion = kitch_sq/full_sq)
  
  # extra area
  train <- train %>% 
    mutate(extra_area = full_sq - life_sq)
  
  # age of house at time of sale
  train <- train %>% 
    mutate(age_at_sale = interval(make_date(year=build_year),timestamp) / years(1))  
  
```

### Grouping appartments together
Some appartments seem to be in the same building. They have the same sub_area and distance to metro.
```{r}
  # assign a common name to them
  train <- train %>% 
    mutate(appartment_name = factor(str_c(sub_area,format(metro_km_avto,digits=3))))
  
  # get the number of appartments in group
  train <- train %>% 
    group_by(appartment_name) %>% 
    tally() %>% 
    right_join(train,by="appartment_name")

```



### General sale characteristics
```{r }
  # number of sales per year_month
  train <- train %>% 
    group_by(year_month) %>% 
    summarize(n_sales_permonth = n()) %>% 
    right_join(train,by="year_month")
```

### Sub Area characteristics

#### Location data
For the location data you have to read in an [external data file](https://www.kaggle.com/jtremoureux/administrative-divisions-of-moscow). You can find a tutorial [here](https://www.kaggle.com/product-feedback/32423#post179905).

```{r warning=FALSE, message=FALSE, eval=FALSE}
  # Longitude and Latitude
  library(rgdal) # read the shapefile with readOGR()
  shp <- readOGR(dsn = "../input/administrative-divisions-of-moscow", layer = "moscow_adm")
  centroids <- coordinates(shp)  
  sub_area <- shp$RAION
  okrug <- shp$OKRUGS
  location_data <- data.frame(sub_area = sub_area, okrug = okrug, longitude=centroids[,1], latitude=centroids[,2])
  train <- train %>% 
    left_join(location_data,by="sub_area")
  
  # Calculate distance from Kremlin for each sub_area
  library(geosphere)
  kremlin = data.frame(longitude = 37.617664,latitude = 55.752121)
  train <- train %>% 
    group_by(sub_area) %>% 
    top_n(n = 1, wt=id) %>% 
    ungroup %>% 
    mutate(distance_from_kremlin = distm(.[c("longitude","latitude")], kremlin, fun=distHaversine)) %>% 
    select(sub_area, distance_from_kremlin) %>% 
    right_join(train, by="sub_area")

```


#### General price level of Sub Areas
```{r eval =F}
  # average price per raion
  train <- train %>% 
    group_by(sub_area) %>% 
    summarize(mean_price_raion = mean(price_doc)) %>% 
    right_join(train,by="sub_area")

  # average price per raion per year
  train <- train %>% 
    group_by(sub_area, year) %>% 
    summarize(mean_price_raion_year = mean(price_doc)) %>% 
    right_join(train,by="sub_area")
  
  # average price per sqm per raion
  train <- train %>% 
    group_by(sub_area) %>% 
    summarize(mean_price_persqm_raion = mean(price_doc/full_sq, na.rm=T)) %>% 
    right_join(train,by="sub_area")
  
```

#### Population characteristics
```{r }
  # population density per raion (i.e. Number of people per square meter)
  train <- train %>% 
    mutate(pop_density_raion = raion_popul/area_m)
  
  # Demographic structure of the raions
  train <- train %>% 
    mutate(young_proportion = young_all/full_all) # proportion of people younger than working age
  train <- train %>% 
    mutate(work_proportion = work_all/full_all) # proportion of people in working age
  train <- train %>% 
    mutate(retire_proportion = ekder_all/full_all) # proportion of people older than working age

```

#### Building information
```{r }
  # average building height per raion
  train <- train %>% 
    group_by(sub_area) %>% 
    summarize(mean_building_height = mean(max_floor,na.rm=T)) %>% 
    right_join(train,by="sub_area")

  # Proportion of houses with certain build materials (e.g. 10% build_count_wood)
  train<-train %>% 
    mutate_each(funs(pct = (.)/raion_build_count_with_builddate_info),matches('^build_count_[a-zA-Z]*$'))
```

#### Educational characteristics
```{r }
  # ratio of number of pupils and preschool seats
  train <- train %>% 
    mutate(ratio_preschool = children_preschool / preschool_quota)

  # ratio of number of pupils and school seats
  train <- train %>% 
    mutate(ratio_school = children_school / school_quota)

```


### dataset related features
```{r}
  # number of missing values per row (this is going to take a while)
  train <- train %>% 
    mutate(count_na_perrow = apply(., 1, function(x) sum(is.na(x))))
```


### Current To-do List

1. Sales (by year or month) for grouped appartments.


#### Disclaimer
1. Not all of these features are going to help your model prediction. So choose yours wisely.
2. For consistency, I will demonstrate all these features for the train set only, while for some features it would make sense to calculate them for the full dataset
3. For easier readibility, I do only minimal data cleaning in this kernel. As the new features are e.g. combinations of the basic features, it would make sense to properly clean those first.
4. While I added some features on my own, most of the features were developed by someone else. As it is not easy to figure out who had the idea first, unfortunately I cannot give you proper credt. So for all of those who shared their ideas: my gratitude goes to you. 



