---
title: "An Updated Collection of New Features"
author: "Philipp Spachtholz"
output:
  html_document:
    fig_height: 4
    fig_width: 7
    theme: paper
---

There are already a lot of good ideas for feature engineering around for this competition. However, they are all scattered across
different kernels and discussion threads.**Therefore, my plan here is to provide an easily accessible and extensible list of ideas for feature engineering (together with their implementation in R).**

```
Recent updates:
- added Feature Importance Analysis
- added more Data cleaning
- grouped appartments in the same building complex together
```

Feel free to add new ideas in the comments and
I'll add them to the list and please don't forget to **upvote** if you find it useful :-).

Having said all that, let's jump right into it:

### Initialization
```{r message=FALSE, warning=FALSE}
  library(data.table)
  library(dplyr)
  library(lubridate)
  library(stringr)
  library(caret)
  library(Matrix)
  library(xgboost)
  library(geosphere)
  library(rgdal)

  train <- fread('../input/train.csv')
  test <- fread('../input/test.csv')
  
  test_id <- test$id
  
```


## Price Doc
```{r}
train %>% count(price_doc) %>% filter(price_doc <= 3000000) %>% arrange(desc(n))

#potentially remove these rows from train set
train <- train %>% mutate(strange_price = ifelse(price_doc %in% c(990000,999000,1000000,1100000,2000000,3000000), 1,0))

train <- train %>% filter(price_doc <= 9e07)
```

## Full square
```{r}

train <- train %>% mutate(full_sq = ifelse(full_sq > 1000, full_sq/100, full_sq))
train <- train %>% mutate(full_sq = ifelse(full_sq > 100 & product_type=="OwnerOccupier" & num_room <= 2, full_sq/10, full_sq))
train <- train %>% mutate(full_sq = ifelse(full_sq > 300 & product_type=="Investment", full_sq/10, full_sq))

test <- test %>% mutate(full_sq = ifelse(full_sq > 300 & product_type=="OwnerOccupier" & num_room <= 2, full_sq/10, full_sq))

train <- train %>% mutate(strange_full_sq = ifelse(full_sq <= 9, full_sq+1,0), full_sq = ifelse(full_sq <= 9, NA, full_sq))

test <- test %>% mutate(strange_full_sq = ifelse(full_sq <= 9, full_sq+1,0), full_sq = ifelse(full_sq <= 9, NA, full_sq))
```

## Living area 
```{r}

train <- train %>% mutate(life_sq = ifelse(life_sq > 1000, life_sq/100, life_sq))
train <- train %>% mutate(life_sq = ifelse(life_sq/10==full_sq, life_sq/10, life_sq))
train <- train %>% mutate(life_sq = ifelse((full_sq >0 & life_sq/full_sq > 4), life_sq/10, life_sq))

test <- test %>% mutate(life_sq = ifelse(life_sq/10==full_sq, life_sq/10, life_sq))
test <- test %>% mutate(life_sq = ifelse((full_sq >0 & life_sq/full_sq > 4), life_sq/10, life_sq))

### swapped vlaues between life and full_sq
train[train$life_sq>train$full_sq & !(is.na(train$life_sq) | is.na(train$full_sq)),c("full_sq","life_sq")]<- train[train$life_sq>train$full_sq & !(is.na(train$life_sq) | is.na(train$full_sq)),c("life_sq","full_sq")]

test[test$life_sq>test$full_sq & !(is.na(test$life_sq) | is.na(test$full_sq)),c("full_sq","life_sq")]<- test[test$life_sq>test$full_sq & !(is.na(test$life_sq) | is.na(test$full_sq)),c("life_sq","full_sq")]

train <- train %>% mutate(strange_life_sq = ifelse(life_sq < 7, life_sq+1,0), life_sq = ifelse(life_sq <= 1, NA, life_sq))

test <- test %>% mutate(strange_life_sq = ifelse(life_sq <= 1, life_sq+1,0), strange_life_sq= ifelse(is.na(strange_life_sq),0,strange_life_sq), life_sq = ifelse(life_sq <= 1, NA, life_sq))

```



## Kitchen area 
```{r}

## build years in kitch_sq
train <- train %>% mutate(build_year = ifelse(kitch_sq>1900,kitch_sq,build_year))
test <- test %>% mutate(build_year = ifelse(kitch_sq>1900,kitch_sq,build_year))

## sometimes kitch_sq >= full_sq
train <- train %>% mutate(kitch_sq = ifelse(kitch_sq >= full_sq, NA, kitch_sq))
test <- test %>% mutate(kitch_sq = ifelse(kitch_sq >= full_sq, NA, kitch_sq))

### kitch_sq >= life_sq
train <- train %>% mutate(kitch_sq = ifelse(kitch_sq >= life_sq, NA, kitch_sq))
test <- test %>% mutate(kitch_sq = ifelse(kitch_sq >= life_sq, NA, kitch_sq))

train <- train %>% mutate(strange_kitch_sq = ifelse(kitch_sq <= 1, kitch_sq+1,0),kitch_sq = ifelse(kitch_sq <= 1, NA, kitch_sq))
test <- test %>% mutate(strange_kitch_sq = ifelse(kitch_sq <= 1, kitch_sq+1,0),kitch_sq = ifelse(kitch_sq <= 1, NA, kitch_sq))

```



## Number of living rooms
```{r}
train <- train %>% mutate(num_room = ifelse(num_room >= 10 | num_room <= 0, NA, num_room))
test <- test %>% mutate(num_room = ifelse(num_room >= 10 | num_room <= 0, NA, num_room))

```


## build year
```{r}

train <- train %>% mutate(build_year = ifelse(build_year > 1000000, mean(as.numeric(c(str_sub(build_year,1,4),str_sub(build_year,5,8)))), build_year))

train <- train %>% mutate(build_year = ifelse(build_year > 2900, as.numeric(str_c("1",str_sub(build_year,2,4))), build_year))

train <- train %>% mutate(strange_build_year = ifelse(build_year <= 1, build_year+1,0), build_year = ifelse(build_year < 1800, NA, build_year))

test <- test %>% mutate(strange_build_year = ifelse(build_year <= 1, build_year+1,0), build_year = ifelse(build_year < 1800, NA, build_year))


```

## floor
```{r}

train <- train %>% mutate(floor = ifelse(floor > 45, round(floor/10), floor))
test <- test %>% mutate(floor = ifelse(floor > 45, round(floor/10), floor))


### to do: probably some floors of 1 are not real information
```

## max floor
```{r}

train <- train %>% mutate(max_floor = ifelse(max_floor>100, as.numeric(str_sub(max_floor,2,3)),max_floor))

train <- train %>% mutate(strange_max_floor = ifelse(max_floor <= 1, max_floor+1,0), max_floor = ifelse(max_floor > 60 | max_floor <=0, NA, max_floor))

test <- test %>% mutate(strange_max_floor = ifelse(max_floor <= 1, max_floor+1,0), max_floor = ifelse(max_floor > 60 | max_floor <=0, NA, max_floor))

```


## state
```{r}
train <- train %>% mutate(state= ifelse(state>10, round(state/10),state))

train <- train %>% mutate(state = factor(state, exclude=NULL))
test <- test %>% mutate(state = factor(state, exclude=NULL))

```


## material
```{r}
train <- train %>% mutate(material = ifelse(material == 3, NA, material), material=factor(material, exclude=NULL))
test <- test %>% mutate(material = ifelse(material == 3, NA, material), material=factor(material, exclude=NULL))
```


## product_type
```{r}
train <- train %>% mutate(product_type = factor(product_type, exclude=NULL))
#test <- test %>% mutate(product_type = #ifelse(is.na(product_type),"Investment",product_type))

test <- test %>% mutate(product_type = factor(product_type))



```

# Subarea
```{r}
train <- train %>% mutate(sub_area = factor(sub_area, exclude=NULL))
test <- test %>% mutate(sub_area = factor(sub_area, exclude=NULL)) # only 145 Poselenie Klenovskoe not in test set
```


# area_m ok

#### Note: use raion popul, seems more reliable


```{r}
train <- train %>% mutate(school_education_centers_raion_pct = school_education_centers_raion/area_m*1e+06)
test <- test %>% mutate(school_education_centers_raion_pct = school_education_centers_raion/area_m*1e+06)

train <- train %>% mutate(school_education_centers_top_20_raion = ifelse(school_education_centers_top_20_raion>=1,1,0))
test <- test %>% mutate(school_education_centers_top_20_raion = ifelse(school_education_centers_top_20_raion>=1,1,0))

train <- train %>% mutate(hospital_beds_raion_pct = hospital_beds_raion/raion_popul)
test <- test %>% mutate(hospital_beds_raion_pct = hospital_beds_raion/raion_popul)

train <- train %>% mutate(healthcare_centers_raion_pct = healthcare_centers_raion/area_m*1e+06)
test <- test %>% mutate(healthcare_centers_raion_pct = healthcare_centers_raion/area_m*1e+06)

train <- train %>% mutate(university_top_20_raion = ifelse(university_top_20_raion>=1,1,0))
test <- test %>% mutate(university_top_20_raion = ifelse(university_top_20_raion>=1,1,0))

train <- train %>% mutate(sport_objects_raion_pct = sport_objects_raion/area_m*1e+06)
test <- test %>% mutate(sport_objects_raion_pct = sport_objects_raion/area_m*1e+06)

train <- train %>% mutate(additional_education_raion_pct = additional_education_raion/area_m*1e+06)
test <- test %>% mutate(additional_education_raion_pct = additional_education_raion/area_m*1e+06)

train <- train %>% mutate(culture_objects_top_25 = NULL, culture_objects_top_25_raion = ifelse(culture_objects_top_25_raion >=2, 2, ifelse(culture_objects_top_25_raion>=1,1,0)))
test <- test %>% mutate(culture_objects_top_25 = NULL, culture_objects_top_25_raion = ifelse(culture_objects_top_25_raion >=2, 2, ifelse(culture_objects_top_25_raion>=1,1,0)))

train <- train %>% mutate(shopping_centers_raion_pct = shopping_centers_raion/area_m*1e+06)
test <- test %>% mutate(shopping_centers_raion_pct = shopping_centers_raion/area_m*1e+06)

train <- train %>% mutate(office_raion = office_raion/area_m*1e+06)
test <- test %>% mutate(office_raion = office_raion/area_m*1e+06)

train <- train %>% mutate(thermal_power_plant_raion = as.numeric(as.factor(thermal_power_plant_raion)))
test <- test %>% mutate(thermal_power_plant_raion = as.numeric(as.factor(thermal_power_plant_raion)))

train <- train %>% mutate(incineration_raion = as.numeric(as.factor(incineration_raion)))
test <- test %>% mutate(incineration_raion = as.numeric(as.factor(incineration_raion)))

train <- train %>% mutate(oil_chemistry_raion = as.numeric(as.factor(oil_chemistry_raion)))
test <- test %>% mutate(oil_chemistry_raion = as.numeric(as.factor(oil_chemistry_raion)))

train <- train %>% mutate(radiation_raion = as.numeric(as.factor(radiation_raion)))
test <- test %>% mutate(radiation_raion = as.numeric(as.factor(radiation_raion)))

train <- train %>% mutate(railroad_terminal_raion = as.numeric(as.factor(railroad_terminal_raion)))
test <- test %>% mutate(railroad_terminal_raion = as.numeric(as.factor(railroad_terminal_raion)))

train <- train %>% mutate(big_market_raion = as.numeric(as.factor(big_market_raion)))
test <- test %>% mutate(big_market_raion = as.numeric(as.factor(big_market_raion)))

train <- train %>% mutate(nuclear_reactor_raion = as.numeric(as.factor(nuclear_reactor_raion)))
test <- test %>% mutate(nuclear_reactor_raion = as.numeric(as.factor(nuclear_reactor_raion)))

train <- train %>% mutate(detention_facility_raion = as.numeric(as.factor(detention_facility_raion)))
test <- test %>% mutate(detention_facility_raion = as.numeric(as.factor(detention_facility_raion)))
```

#### Convert to same data type many doubles in test, no doubles in train
```{r}
names(train) <- str_replace_all(names(train),"^[0-9]","a_")
names(train) <- str_replace_all(names(train),"-","_")
names(test) <- str_replace_all(names(test),"^[0-9]","a_")
names(test) <- str_replace_all(names(test),"-","_")
train <- train %>% mutate_if(is.numeric,as.double)
test <- test %>% mutate_if(is.numeric,as.double)

```


```{r}
train <- train %>% mutate(train_test = "train")
test <- test %>% mutate(train_test = "test")
full <- bind_rows(train,test)
```



## Look at distribution of features between train and test

```{r}
full %>% ggplot(aes(x=full_sq)) + geom_line(stat="density", aes(color=train_test),size=1.2, trim=T)+geom_rug()+facet_grid(product_type~.)+coord_cartesian(xlim=c(10,200))
```
```{r}
full %>% ggplot(aes(x=life_sq)) + stat_density(geom="line", aes(group=train_test,color=train_test),size=1.2,na.rm=T, trim=T)+facet_grid(product_type~.)+coord_cartesian(xlim=c(0,100))
```
```{r}
full %>% ggplot(aes(x=kitch_sq)) + stat_density(geom="line", aes(group=train_test,color=train_test),size=1.2,na.rm=T, trim=T)+facet_grid(product_type~.)+coord_cartesian(xlim=c(0,25))
```


## Engineering

### Time features

#### Split the timestamp feature

```{r }
  # year
  train <- train %>% 
    mutate(year = year(timestamp))
  test <- test %>% 
    mutate(year = year(timestamp))

  # year_month
  train <- train %>% 
    mutate(year_month = make_date(year(timestamp),month(timestamp)))
  test <- test %>% 
    mutate(year_month = make_date(year(timestamp),month(timestamp)))  
```


#### Get month, week, weekday

```{r }
  # month of year
  train <- train %>% mutate(month_of_year = month(timestamp))
  test <- test %>% mutate(month_of_year = month(timestamp))

  # week of year
  train <- train %>% mutate(week_of_year = week(timestamp))
  test <- test %>% mutate(week_of_year = week(timestamp))  

  # day of month
  train <- train %>% mutate(day_of_month = mday(timestamp))
  test <- test %>% mutate(day_of_month = mday(timestamp))  
  
  # weekday
  train <- train %>% mutate(day_of_week = wday(timestamp))
  test <- test %>% mutate(day_of_week = wday(timestamp))  

```


### House characteristics


```{r }
  # number of floors to the top of house
  train <- train %>% mutate(floor_from_top = max_floor - floor)
  test <- test %>% mutate(floor_from_top = max_floor - floor)
  
  # relative position of floor in house
  train <- train %>% mutate(floor_by_maxfloor = floor/max_floor)
  test <- test %>% mutate(floor_by_maxfloor = floor/max_floor)  
  
  # average room size
  train <- train %>% mutate(roomsize = (life_sq-kitch_sq)/num_room) 
  test <- test %>% mutate(roomsize = (life_sq-kitch_sq)/num_room)   
  
  # relative proportion of living area
  train <- train %>% mutate(life_proportion = life_sq/full_sq)
  test <- test %>% mutate(life_proportion = life_sq/full_sq)  
  
  # relative proportion of kitchen area
  train <- train %>% mutate(kitchen_proportion = kitch_sq/full_sq)
  test <- test %>% mutate(kitchen_proportion = kitch_sq/full_sq)  
  
  # extra area
  train <- train %>% mutate(extra_area = full_sq - life_sq)
  test <- test %>% mutate(extra_area = full_sq - life_sq)  
  
  # age of house at time of sale
  train <- train %>% mutate(age_at_sale = interval(make_date(year=build_year),timestamp) / years(1))  
  test <- test %>% mutate(age_at_sale = interval(make_date(year=build_year),timestamp) / years(1))    
  
```

### Grouping appartments together
Some appartments seem to be in the same building. They have the same sub_area and distance to metro.
```{r}
  # assign a common name to them
  train <- train %>% mutate(appartment_name = factor(str_c(sub_area,format(metro_km_avto,digits=3))))
  test <- test %>% mutate(appartment_name = factor(str_c(sub_area,format(metro_km_avto,digits=3))))
  
  # get the number of appartments in group
  train <- train %>% 
    group_by(appartment_name) %>% 
    tally() %>% 
    right_join(train,by="appartment_name")

  test <- test %>% 
    group_by(appartment_name) %>% 
    tally() %>% 
    right_join(test,by="appartment_name")
```



### General sale characteristics
```{r }
  # number of sales per year_month
  train <- train %>% 
    group_by(year_month) %>% 
    summarize(n_sales_permonth = n()) %>% 
    right_join(train,by="year_month")

  test <- test %>% 
    group_by(year_month) %>% 
    summarize(n_sales_permonth = n()) %>% 
    right_join(test,by="year_month")

```

### Sub Area characteristics

#### Location data
For the location data you have to read in an [external data file](https://www.kaggle.com/jtremoureux/administrative-divisions-of-moscow). You can find a tutorial [here](https://www.kaggle.com/product-feedback/32423#post179905).

```{r warning=FALSE, message=FALSE}
  # Longitude and Latitude
  shp <- readOGR(dsn = "../input/administrative-divisions-of-moscow", layer = "moscow_adm")
  centroids <- coordinates(shp)
  sub_area <- shp$RAION
  okrug <- shp$OKRUGS
  location_data <- data.frame(sub_area = sub_area, okrug = okrug, longitude=centroids[,1], latitude=centroids[,2])

  train <- train %>%
    left_join(location_data,by="sub_area")

  test <- test %>%
    left_join(location_data,by="sub_area")

  
  # Calculate distance and angle from Kremlin for each sub_area
  kremlin = data.frame(longitude = 37.617664,latitude = 55.752121)
  train <- train %>%
    group_by(sub_area) %>%
    top_n(n = 1, wt=id) %>%
    ungroup %>%
    mutate(distance_from_kremlin = distm(.[c("longitude","latitude")], kremlin, fun=distHaversine)/1000, angle_from_kremlin = bearing(.[c("longitude","latitude")], kremlin)) %>%
    select(sub_area, distance_from_kremlin, angle_from_kremlin) %>%
    right_join(train, by="sub_area")
  
  train <- train %>% mutate(bearing.x = cos(pi/180*angle_from_kremlin), bearing.y = sin(pi/180*angle_from_kremlin), bearing.xy = bearing.x*bearing.y)
  
test <- test %>%
    group_by(sub_area) %>%
    top_n(n = 1, wt=id) %>%
    ungroup %>%
    mutate(distance_from_kremlin = distm(.[c("longitude","latitude")], kremlin, fun=distHaversine)/1000, angle_from_kremlin = bearing(.[c("longitude","latitude")], kremlin)) %>%
    select(sub_area, distance_from_kremlin, angle_from_kremlin) %>%
    right_join(test, by="sub_area")
  
  test <- test %>% mutate(bearing.x = cos(pi/180*angle_from_kremlin), bearing.y = sin(pi/180*angle_from_kremlin), bearing.xy = bearing.x*bearing.y)
  

```


#### General price level of Sub Areas
```{r}
  # average price per raion
  train <- train %>% 
    group_by(sub_area) %>% 
    summarize(mean_price_raion = mean(price_doc)) %>% 
    right_join(train,by="sub_area")

  # average price per raion per year
  train <- train %>% 
    group_by(sub_area, year) %>% 
    summarize(mean_price_raion_year = mean(price_doc)) %>% 
    right_join(train,by=c("sub_area","year"))
  
  # average price per sqm per raion
  train <- train %>% 
    group_by(sub_area) %>% 
    summarize(mean_price_persqm_raion = mean(price_doc/full_sq, na.rm=T)) %>% 
    right_join(train,by="sub_area")
  
  # average price rank per raion
  train <- train %>% group_by(sub_area) %>% mutate(price_rank_raion = rank(mean_price_raion))
  test <- train %>% group_by(sub_area) %>% summarize(price_rank_raion = mean(price_rank_raion)) %>% select(sub_area,price_rank_raion) %>% right_join(test, by="sub_area")  
```

#### Population characteristics
```{r }
  # population density per raion (i.e. Number of people per square meter)
  train <- train %>% mutate(pop_density_raion = raion_popul/area_m)
  test <- test %>% mutate(pop_density_raion = raion_popul/area_m)
  
  # Demographic structure of the raions
  train <- train %>% mutate(young_proportion = young_all/full_all) # proportion of people younger than working age
  test <- test %>% mutate(young_proportion = young_all/full_all) # proportion of people younger than working age  
  train <- train %>% mutate(work_proportion = work_all/full_all) # proportion of people in working age
  test <- test %>% mutate(work_proportion = work_all/full_all) # proportion of people in working age  
  train <- train %>% mutate(retire_proportion = ekder_all/full_all) # proportion of people older than working age
  test <- test %>% mutate(retire_proportion = ekder_all/full_all) # proportion of people older than working age  

```

#### Building information
```{r }
  # average building height per raion
  train <- full %>% 
    group_by(sub_area) %>% 
    summarize(mean_building_height = mean(max_floor,na.rm=T)) %>% 
    right_join(train,by="sub_area")
  test <- full %>% 
    group_by(sub_area) %>% 
    summarize(mean_building_height = mean(max_floor,na.rm=T)) %>% 
    right_join(test,by="sub_area")

  # Proportion of houses with certain build materials (e.g. 10% build_count_wood)
  train<-train %>%  mutate_each(funs(pct = (.)/raion_build_count_with_builddate_info),matches('^build_count_[a-zA-Z]*$'))
  test<-test %>%  mutate_each(funs(pct = (.)/raion_build_count_with_builddate_info),matches('^build_count_[a-zA-Z]*$'))
  
```

#### Educational characteristics
```{r }
  # ratio of number of pupils and preschool seats
  train <- train %>% mutate(ratio_preschool = children_preschool / preschool_quota)
  test <- test %>% mutate(ratio_preschool = children_preschool / preschool_quota)

  # ratio of number of pupils and school seats
  train <- train %>% mutate(ratio_school = children_school / school_quota)
  test <- test %>% mutate(ratio_school = children_school / school_quota)  

```


### dataset related features
```{r}
  # number of missing values per row (this is going to take a while)
  train <- train %>% mutate(count_na_perrow = apply(., 1, function(x) sum(is.na(x))))
  test <- test %>% mutate(count_na_perrow = apply(., 1, function(x) sum(is.na(x))))
```


## normalize price_doc

```{r}

mean_prices <- train %>% group_by(year_month) %>% summarize(mean_prices=mean(price_doc))

train <- train %>% left_join(mean_prices, by=c("year_month"))

overall_mean <- train %>% filter(year>=2015) %>%  summarize(overall_mean=mean(price_doc)) %>% .[[1]]

train <- train %>% mutate(price_normal = price_doc-mean_prices+overall_mean)

```

### Feature Importance
#### Features
```{r}
outcomes <- train %>% filter(strange_price == 0) %>% select(price_normal) %>% .[[1]]
#outcomes <- train %>% select(price_doc) %>% .[[1]]

basic_features <- c("full_sq", "life_sq", "kitch_sq", "num_room", "floor", "max_floor", "material", "build_year", "state", "product_type")

#basic_features <- setdiff(names(train),c("id","timestamp","year","year_month","appartment_name","mean_price_persqm_raion","mean_price_raion_year","mean_price_raion","price_rank_raion","sub_area","price_doc"))

new_features <- c("month_of_year","week_of_year", "day_of_month", "day_of_week", "floor_from_top", "floor_by_maxfloor", "roomsize", "life_proportion", "kitchen_proportion", "extra_area", "age_at_sale", "n_sales_permonth", "distance_from_kremlin", "young_proportion", "work_proportion", "retire_proportion", "mean_building_height", "ratio_preschool",
"ratio_school", "count_na_perrow", "angle_from_kremlin", "bearing.x", "bearing.y", "bearing.xy", "pop_density_raion", "school_education_centers_raion_pct", "hospital_beds_raion_pct", "healthcare_centers_raion_pct", "sport_objects_raion_pct", "additional_education_raion_pct", "shopping_centers_raion_pct", "okrug")

exclude_features <- c("price_normal","mean_prices", "count_na_perrow", "train_test", "price_doc", "timestamp", "id", "mean_price_raion_year", "mean_price_raion", "mean_price_persqm_raion", "year", "year_month", "sub_area", "appartment_name", "n", "strange_price")

```




## Importance Analysis
```{r, echo=FALSE, message=FALSE, warning=FALSE}
  #predictors <- c(basic_features,new_features)
  #predictors <- basic_features
  predictors <- setdiff(names(train), exclude_features)


  train_set <- train %>% filter(strange_price == 0) %>% select(one_of(predictors))
#  train_set <- train %>% select(one_of(predictors))
  
  test_set <- test %>% select(one_of(predictors))

  dummy <- dummyVars(~.,train_set)
  train_matrix <- predict(dummy,train_set)
  test_matrix <- predict(dummy,test_set)

  train_sparse <- Matrix(train_matrix,sparse = T)
  test_sparse <- Matrix(test_matrix, sparse=T)
  
  dtrain <- xgb.DMatrix(data = train_sparse,label=log(outcomes+1))
  dtest <- xgb.DMatrix(data = test_sparse)  

  #### xgboost params
  param <- list(objective="reg:linear",
              eval_metric = "rmse",
              eta = .1,
              max_depth = 4,
              gamma = 1,
              subsample = 0.7,
              colsample_bytree = .7
  )

  # CV for number of rounds
  xgb_cv <- xgb.cv(data = dtrain,
                  nfold = 5,
                  params = param,
                  nrounds = 150000,
                  maximize = FALSE,
                  prediction = TRUE,
                  early.stop.round = 50,
                  print_every_n = 50,
                  verbose = 1
  )
  rounds <- xgb_cv$best_iteration  
  
  # Train model
  xgb_model <- xgb.train(data = dtrain,
                       params = param,
                       watchlist = list(train = dtrain),
                       nrounds = rounds,
                       verbose = 0
  )

  imp_matrix_all <- xgb.importance(colnames(train_sparse),xgb_model)

```

We can see that our work payed off. There are several new features having higher importance than the basic features. 
What we also see is that the time features (e.g., day of week) don't seem too important. 

```{r, fig.height=10, width=10, echo=FALSE}
  imp_matrix_all <- imp_matrix_all %>% mutate(group = ifelse(Feature %in% new_features,"new","old"))

  ggplot(head(imp_matrix_all,20),aes(x=reorder(Feature,Gain),y=Gain, fill=group))+geom_bar(stat="identity")+coord_flip(ylim=c(0,0.2))+theme_bw()+labs(x="")
```

### make prediction

```{r}
preds <- data.frame(id=test_id, price_doc = exp(predict(xgb_model,dtest))-1)

#preds$price_doc <- preds$price_doc / (mean(preds$price_doc)/7110466)
preds$price_doc <- preds$price_doc * (6600466/mean(train$price_normal))

write.csv(preds, '../submission.csv', row.names = FALSE, quote = FALSE)
```

### predict product_type in test set

```{r}

train_set <- test_set %>% filter(!is.na(product_type))
outcomes <- as.numeric(train_set$product_type)-1
train_set <- train_set %>% select(-product_type)



test_set <- test_set %>% filter(is.na(product_type)) %>% select(-product_type)

train_set <- train_set %>% mutate_if(is.character, as.factor)
test_set <- test_set %>% mutate_if(is.character,as.factor)
train_set$railroad_1line <- NULL
test_set$railroad_1line <- NULL

dummy <- dummyVars(~.,train_set)
train_matrix <- predict(dummy, train_set)
train_sparse <- Matrix(train_matrix,sparse=TRUE)
test_matrix <- predict(dummy, test_set)
test_sparse <- Matrix(test_matrix,sparse=TRUE)

dtrain <- xgb.DMatrix(data = train_sparse,label=outcomes)
dtest <- xgb.DMatrix(data = test_sparse)

  #### xgboost params
  param <- list(objective="binary:logistic",
              eval_metric = "auc",
              eta = .1,
              max_depth = 5,
              subsample = 0.7,
              colsample_bytree = .7
  )

  # CV for number of rounds
  xgb_cv <- xgb.cv(data = dtrain,
                  nfold = 5,
                  params = param,
                  nrounds = 150000,
                  maximize = TRUE,
                  prediction = TRUE,
                  early.stop.round = 50,
                  print_every_n = 50,
                  verbose = 1
  )
  rounds <- xgb_cv$best_iteration  
  
  # Train model
  xgb_model <- xgb.train(data = dtrain,
                       params = param,
                       watchlist = list(train = dtrain),
                       nrounds = rounds,
                       verbose = 0
  )

  predict(xgb_model,dtest)>0.5
  
    imp_matrix_all <- xgb.importance(colnames(train_sparse),xgb_model)
ggplot(head(imp_matrix_all,20),aes(x=reorder(Feature,Gain),y=Gain))+geom_bar(stat="identity")+coord_flip(ylim=c(0,0.2))+theme_bw()+labs(x="")
```


### Current To-do List

1. Sales (by year or month) for grouped appartments.


#### Disclaimer
1. Not all of these features are going to help your model prediction. So choose yours wisely.
2. For consistency, I will demonstrate all these features for the train set only, while for some features it would make sense to calculate them for the full dataset
3. For easier readibility, I do only minimal data cleaning in this kernel. As the new features are e.g. combinations of the basic features, it would make sense to properly clean those first.
4. While I added some features on my own, most of the features were developed by someone else. As it is not easy to figure out who had the idea first, unfortunately I cannot give you proper credt. So for all of those who shared their ideas: my gratitude goes to you. 



