---
title: "Prediction Notebook"
author: "Philipp Spachtholz"
output:
  html_document:
    fig_height: 4
    fig_width: 7
    theme: paper
---

# todo: price per sqm outliers
# todo: full_sq na in test set

### Initialization
```{r message=FALSE, warning=FALSE}
  library(data.table)
  library(dplyr)
  library(lubridate)
  library(stringr)
  library(caret)
  library(Matrix)
  library(xgboost)
  library(geosphere)
  library(rgdal)

  train <- fread('../input/train.csv')
  test <- fread('../input/test.csv')
  macro <- fread('../input/macro.csv')
  
  test_id <- test$id
  
```


## Price Doc
```{r}
train %>% count(price_doc) %>% filter(price_doc <= 3000000) %>% arrange(desc(n))

#potentially remove these rows from train set
train <- train %>% mutate(strange_price = ifelse(price_doc %in% c(990000,999000,1000000,1100000,2000000,3000000), 1,0))

train <- train %>% filter(price_doc <= 9e07)
```

<!-- ## Full square -->
<!-- ```{r} -->

<!-- train <- train %>% mutate(full_sq = ifelse(full_sq > 1000, full_sq/100, full_sq)) -->
<!-- train <- train %>% mutate(full_sq = ifelse(full_sq > 100 & product_type=="OwnerOccupier" & num_room <= 2, full_sq/10, full_sq)) -->
<!-- train <- train %>% mutate(full_sq = ifelse(full_sq > 300 & product_type=="Investment", full_sq/10, full_sq)) -->

<!-- test <- test %>% mutate(full_sq = ifelse(full_sq > 300 & product_type=="OwnerOccupier" & num_room <= 2, full_sq/10, full_sq)) -->

<!-- train <- train %>% mutate(strange_full_sq = ifelse(full_sq <= 9, full_sq+1,0), full_sq = ifelse(full_sq <= 9, NA, full_sq)) -->

<!-- test <- test %>% mutate(strange_full_sq = ifelse(full_sq <= 9, full_sq+1,0), full_sq = ifelse(full_sq <= 9, NA, full_sq)) -->



<!-- ``` -->

## Living area 
```{r}

train <- train %>% mutate(life_sq = ifelse(life_sq > 1000, life_sq/100, life_sq))
train <- train %>% mutate(life_sq = ifelse(life_sq/10==full_sq, life_sq/10, life_sq))
train <- train %>% mutate(life_sq = ifelse((full_sq >0 & life_sq/full_sq > 4), life_sq/10, life_sq))

test <- test %>% mutate(life_sq = ifelse(life_sq/10==full_sq, life_sq/10, life_sq))
test <- test %>% mutate(life_sq = ifelse((full_sq >0 & life_sq/full_sq > 4), life_sq/10, life_sq))

### swapped vlaues between life and full_sq
train[train$life_sq>train$full_sq & !(is.na(train$life_sq) | is.na(train$full_sq)),c("full_sq","life_sq")]<- train[train$life_sq>train$full_sq & !(is.na(train$life_sq) | is.na(train$full_sq)),c("life_sq","full_sq")]

test[test$life_sq>test$full_sq & !(is.na(test$life_sq) | is.na(test$full_sq)),c("full_sq","life_sq")]<- test[test$life_sq>test$full_sq & !(is.na(test$life_sq) | is.na(test$full_sq)),c("life_sq","full_sq")]

train <- train %>% mutate(strange_life_sq = ifelse(life_sq < 7, life_sq+1,0), life_sq = ifelse(life_sq <= 1, NA, life_sq))

test <- test %>% mutate(strange_life_sq = ifelse(life_sq <= 1, life_sq+1,0), strange_life_sq= ifelse(is.na(strange_life_sq),0,strange_life_sq), life_sq = ifelse(life_sq <= 1, NA, life_sq))

```



## Kitchen area 
```{r}

## build years in kitch_sq
train <- train %>% mutate(build_year = ifelse(kitch_sq>1900,kitch_sq,build_year))
test <- test %>% mutate(build_year = ifelse(kitch_sq>1900,kitch_sq,build_year))

## sometimes kitch_sq >= full_sq
train <- train %>% mutate(kitch_sq = ifelse(kitch_sq >= full_sq, NA, kitch_sq))
test <- test %>% mutate(kitch_sq = ifelse(kitch_sq >= full_sq, NA, kitch_sq))

### kitch_sq >= life_sq
train <- train %>% mutate(kitch_sq = ifelse(kitch_sq >= life_sq, NA, kitch_sq))
test <- test %>% mutate(kitch_sq = ifelse(kitch_sq >= life_sq, NA, kitch_sq))

train <- train %>% mutate(strange_kitch_sq = ifelse(kitch_sq <= 1, kitch_sq+1,0),kitch_sq = ifelse(kitch_sq <= 1, NA, kitch_sq))
test <- test %>% mutate(strange_kitch_sq = ifelse(kitch_sq <= 1, kitch_sq+1,0),kitch_sq = ifelse(kitch_sq <= 1, NA, kitch_sq))

```



## Number of living rooms
```{r}
train <- train %>% mutate(num_room = ifelse(num_room >= 10 | num_room <= 0, NA, num_room))
test <- test %>% mutate(num_room = ifelse(num_room >= 10 | num_room <= 0, NA, num_room))

```


## build year
```{r}

train <- train %>% mutate(build_year = ifelse(build_year > 1000000, mean(as.numeric(c(str_sub(build_year,1,4),str_sub(build_year,5,8)))), build_year))

train <- train %>% mutate(build_year = ifelse(build_year > 2900, as.numeric(str_c("1",str_sub(build_year,2,4))), build_year))

train <- train %>% mutate(strange_build_year = ifelse(build_year <= 1, build_year+1,0), build_year = ifelse(build_year < 1800, NA, build_year))

test <- test %>% mutate(strange_build_year = ifelse(build_year <= 1, build_year+1,0), build_year = ifelse(build_year < 1800, NA, build_year))


```

## floor
```{r}

train <- train %>% mutate(floor = ifelse(floor > 45, round(floor/10), floor))
test <- test %>% mutate(floor = ifelse(floor > 45, round(floor/10), floor))


### to do: probably some floors of 1 are not real information
```

## max floor
```{r}

train <- train %>% mutate(max_floor = ifelse(max_floor>100, as.numeric(str_sub(max_floor,2,3)),max_floor))

train <- train %>% mutate(strange_max_floor = ifelse(max_floor <= 1, max_floor+1,0), max_floor = ifelse(max_floor > 60 | max_floor <=0, NA, max_floor))

test <- test %>% mutate(strange_max_floor = ifelse(max_floor <= 1, max_floor+1,0), max_floor = ifelse(max_floor > 60 | max_floor <=0, NA, max_floor))

```


## state
```{r}
train <- train %>% mutate(state= ifelse(state>10, round(state/10),state))

train <- train %>% mutate(state = factor(state, exclude=NULL))
test <- test %>% mutate(state = factor(state, exclude=NULL))

```


## material
```{r}
train <- train %>% mutate(material = ifelse(material == 3, NA, material), material=factor(material, exclude=NULL))
test <- test %>% mutate(material = ifelse(material == 3, NA, material), material=factor(material, exclude=NULL))
```


## product_type
```{r}
train <- train %>% mutate(product_type = as.factor(product_type))

test <- test %>% mutate(product_type = as.factor(product_type))

```

# Subarea
```{r}
train <- train %>% mutate(sub_area = factor(sub_area, exclude=NULL))
test <- test %>% mutate(sub_area = factor(sub_area, exclude=NULL)) # only 145 Poselenie Klenovskoe not in test set
```


# area_m ok

#### Note: use raion popul, seems more reliable


```{r}
train <- train %>% mutate(school_education_centers_raion_pct = school_education_centers_raion/area_m*1e+06)
test <- test %>% mutate(school_education_centers_raion_pct = school_education_centers_raion/area_m*1e+06)

train <- train %>% mutate(school_education_centers_top_20_raion = ifelse(school_education_centers_top_20_raion>=1,1,0))
test <- test %>% mutate(school_education_centers_top_20_raion = ifelse(school_education_centers_top_20_raion>=1,1,0))

train <- train %>% mutate(hospital_beds_raion_pct = hospital_beds_raion/raion_popul)
test <- test %>% mutate(hospital_beds_raion_pct = hospital_beds_raion/raion_popul)

train <- train %>% mutate(healthcare_centers_raion_pct = healthcare_centers_raion/area_m*1e+06)
test <- test %>% mutate(healthcare_centers_raion_pct = healthcare_centers_raion/area_m*1e+06)

train <- train %>% mutate(university_top_20_raion = ifelse(university_top_20_raion>=1,1,0))
test <- test %>% mutate(university_top_20_raion = ifelse(university_top_20_raion>=1,1,0))

train <- train %>% mutate(sport_objects_raion_pct = sport_objects_raion/area_m*1e+06)
test <- test %>% mutate(sport_objects_raion_pct = sport_objects_raion/area_m*1e+06)

train <- train %>% mutate(additional_education_raion_pct = additional_education_raion/area_m*1e+06)
test <- test %>% mutate(additional_education_raion_pct = additional_education_raion/area_m*1e+06)

train <- train %>% mutate(culture_objects_top_25 = NULL, culture_objects_top_25_raion = ifelse(culture_objects_top_25_raion >=2, 2, ifelse(culture_objects_top_25_raion>=1,1,0)))
test <- test %>% mutate(culture_objects_top_25 = NULL, culture_objects_top_25_raion = ifelse(culture_objects_top_25_raion >=2, 2, ifelse(culture_objects_top_25_raion>=1,1,0)))

train <- train %>% mutate(shopping_centers_raion_pct = shopping_centers_raion/area_m*1e+06)
test <- test %>% mutate(shopping_centers_raion_pct = shopping_centers_raion/area_m*1e+06)

train <- train %>% mutate(office_raion = office_raion/area_m*1e+06)
test <- test %>% mutate(office_raion = office_raion/area_m*1e+06)

train <- train %>% mutate(thermal_power_plant_raion = as.numeric(as.factor(thermal_power_plant_raion)))
test <- test %>% mutate(thermal_power_plant_raion = as.numeric(as.factor(thermal_power_plant_raion)))

train <- train %>% mutate(incineration_raion = as.numeric(as.factor(incineration_raion)))
test <- test %>% mutate(incineration_raion = as.numeric(as.factor(incineration_raion)))

train <- train %>% mutate(oil_chemistry_raion = as.numeric(as.factor(oil_chemistry_raion)))
test <- test %>% mutate(oil_chemistry_raion = as.numeric(as.factor(oil_chemistry_raion)))

train <- train %>% mutate(radiation_raion = as.numeric(as.factor(radiation_raion)))
test <- test %>% mutate(radiation_raion = as.numeric(as.factor(radiation_raion)))

train <- train %>% mutate(railroad_terminal_raion = as.numeric(as.factor(railroad_terminal_raion)))
test <- test %>% mutate(railroad_terminal_raion = as.numeric(as.factor(railroad_terminal_raion)))

train <- train %>% mutate(big_market_raion = as.numeric(as.factor(big_market_raion)))
test <- test %>% mutate(big_market_raion = as.numeric(as.factor(big_market_raion)))

train <- train %>% mutate(nuclear_reactor_raion = as.numeric(as.factor(nuclear_reactor_raion)))
test <- test %>% mutate(nuclear_reactor_raion = as.numeric(as.factor(nuclear_reactor_raion)))

train <- train %>% mutate(detention_facility_raion = as.numeric(as.factor(detention_facility_raion)))
test <- test %>% mutate(detention_facility_raion = as.numeric(as.factor(detention_facility_raion)))
```

#### Convert to same data type many doubles in test, no doubles in train
```{r}
names(train) <- str_replace_all(names(train),"^[0-9]","a_")
names(train) <- str_replace_all(names(train),"-","_")
names(test) <- str_replace_all(names(test),"^[0-9]","a_")
names(test) <- str_replace_all(names(test),"-","_")

```

## Round values in test set to match train set
```{r}
#train <- train %>% mutate(full_sq = round(full_sq, digits=0), life_sq= round(life_sq, digits=0), kitch_sq=round(kitch_sq, digits=0))
#test <- test %>% mutate(full_sq = round(full_sq, digits=0), life_sq= round(life_sq, digits=0), kitch_sq=round(kitch_sq, digits=0))
```


## Tverskoe problem 603 errors

```{r}
train[near(train$kremlin_km,0.07289655),] <- train %>% 
  filter(near(kremlin_km,0.07289655)) %>% 
  mutate_at(13:290,funs(replace(.,1:n(),NA)))

test[near(test$kremlin_km,0.07289655),] <- test %>% 
  filter(near(kremlin_km,0.07289655)) %>% 
  mutate_at(13:290,funs(replace(.,1:n(),NA)))

```


```{r}
train <- train %>% mutate(train_test = "train")
test <- test %>% mutate(train_test = "test")
full <- bind_rows(train,test)
```




## Look at distribution of features between train and test

```{r}
full %>% ggplot(aes(x=full_sq)) + geom_line(stat="density", aes(color=train_test),size=1.2, trim=T)+geom_rug()+facet_grid(product_type~.)+coord_cartesian(xlim=c(10,200))
```
```{r}
full %>% ggplot(aes(x=life_sq)) + stat_density(geom="line", aes(group=train_test,color=train_test),size=1.2,na.rm=T, trim=T)+facet_grid(product_type~.)+coord_cartesian(xlim=c(0,100))
```
```{r}
full %>% ggplot(aes(x=kitch_sq)) + stat_density(geom="line", aes(group=train_test,color=train_test),size=1.2,na.rm=T, trim=T)+facet_grid(product_type~.)+coord_cartesian(xlim=c(0,25))
```


## Engineering

### Time features

#### Split the timestamp feature

```{r }
  # year
  train <- train %>% 
    mutate(year = year(timestamp))
  test <- test %>% 
    mutate(year = year(timestamp))
  
  # quarter
  train <- train %>% mutate(quarter = str_c(year, quarter(timestamp),sep="_"))  
  test <- test %>% mutate(quarter = str_c(year, quarter(timestamp),sep="_"))

  # year_month
  train <- train %>% 
    mutate(year_month = make_date(year(timestamp),month(timestamp)))
  test <- test %>% 
    mutate(year_month = make_date(year(timestamp),month(timestamp)))  
```


#### Get month, week, weekday

```{r }
  # month of year
  train <- train %>% mutate(month_of_year = month(timestamp))
  test <- test %>% mutate(month_of_year = month(timestamp))

  # week of year
  train <- train %>% mutate(week_of_year = week(timestamp))
  test <- test %>% mutate(week_of_year = week(timestamp))  

  # day of month
  train <- train %>% mutate(day_of_month = mday(timestamp))
  test <- test %>% mutate(day_of_month = mday(timestamp))  
  
  # weekday
  train <- train %>% mutate(day_of_week = wday(timestamp))
  test <- test %>% mutate(day_of_week = wday(timestamp))  

```


### House characteristics


```{r }
  # number of floors to the top of house
  train <- train %>% mutate(floor_from_top = max_floor - floor)
  test <- test %>% mutate(floor_from_top = max_floor - floor)
  
  # relative position of floor in house
  train <- train %>% mutate(floor_by_maxfloor = floor/max_floor)
  test <- test %>% mutate(floor_by_maxfloor = floor/max_floor)  
  
  # average room size
  train <- train %>% mutate(roomsize = (life_sq-kitch_sq)/num_room) 
  test <- test %>% mutate(roomsize = (life_sq-kitch_sq)/num_room)   
  
  # relative proportion of living area
  train <- train %>% mutate(life_proportion = life_sq/full_sq)
  test <- test %>% mutate(life_proportion = life_sq/full_sq)  
  
  # relative proportion of kitchen area
  train <- train %>% mutate(kitchen_proportion = kitch_sq/full_sq)
  test <- test %>% mutate(kitchen_proportion = kitch_sq/full_sq)  
  
  # extra area
  train <- train %>% mutate(extra_area = full_sq - life_sq)
  test <- test %>% mutate(extra_area = full_sq - life_sq)  
  
  # age of house at time of sale
  train <- train %>% mutate(age_at_sale = interval(make_date(year=build_year),timestamp) / years(1))  
  test <- test %>% mutate(age_at_sale = interval(make_date(year=build_year),timestamp) / years(1))    
  
```

### Grouping appartments together
Some appartments seem to be in the same building. They have the same sub_area and distance to metro.
```{r}
  # assign a common name to them
  train <- train %>% mutate(appartment_name = factor(str_c(sub_area,format(metro_km_avto,digits=3))))
  test <- test %>% mutate(appartment_name = factor(str_c(sub_area,format(metro_km_avto,digits=3))))
  
  # get the number of appartments in group
  train <- train %>% 
    group_by(appartment_name) %>% 
    tally() %>% 
    right_join(train,by="appartment_name")

  test <- test %>% 
    group_by(appartment_name) %>% 
    tally() %>% 
    right_join(test,by="appartment_name")
```



### General sale characteristics
```{r }
  # number of sales per year_month
  train <- train %>% 
    group_by(year_month) %>% 
    summarize(n_sales_permonth = n()) %>% 
    right_join(train,by="year_month")

  test <- test %>% 
    group_by(year_month) %>% 
    summarize(n_sales_permonth = n()) %>% 
    right_join(test,by="year_month")
  
  # presale
  train <- train %>% 
    mutate(presale = ifelse(build_year>year,1,0))
  test <- test %>% 
    mutate(presale = ifelse(build_year>year,1,0))  

```

### Sub Area characteristics

#### Location data
```{r warning=FALSE, message=FALSE}
  shp <- readOGR(dsn = "../input/administrative-divisions-of-moscow", layer = "moscow_adm")
  centroids <- coordinates(shp)
  sub_area <- shp$RAION
  okrug <- shp$OKRUGS
  location_data <- data.frame(sub_area = sub_area, okrug = okrug, sub_area_lon=centroids[,1], sub_area_lat=centroids[,2])

  train <- train %>%
    left_join(location_data,by="sub_area")

  test <- test %>%
    left_join(location_data,by="sub_area")

  
  # Calculate distance and angle from Kremlin for each sub_area
  kremlin = data.frame(longitude = 37.617664,latitude = 55.752121)
  train <- train %>%
    group_by(sub_area) %>%
    top_n(n = 1, wt=id) %>%
    ungroup %>%
    mutate(distance_from_kremlin = distm(.[c("sub_area_lon","sub_area_lat")], kremlin, fun=distHaversine)/1000, angle_from_kremlin = bearing(.[c("sub_area_lon","sub_area_lat")], kremlin)) %>%
    select(sub_area, distance_from_kremlin, angle_from_kremlin) %>%
    right_join(train, by="sub_area")
  
  train <- train %>% mutate(bearing.x = cos(pi/180*angle_from_kremlin), bearing.y = sin(pi/180*angle_from_kremlin), bearing.xy = bearing.x*bearing.y)
  
test <- test %>%
    group_by(sub_area) %>%
    top_n(n = 1, wt=id) %>%
    ungroup %>%
    mutate(distance_from_kremlin = distm(.[c("sub_area_lon","sub_area_lat")], kremlin, fun=distHaversine)/1000, angle_from_kremlin = bearing(.[c("sub_area_lon","sub_area_lat")], kremlin)) %>%
    select(sub_area, distance_from_kremlin, angle_from_kremlin) %>%
    right_join(test, by="sub_area")
  
  test <- test %>% mutate(bearing.x = cos(pi/180*angle_from_kremlin), bearing.y = sin(pi/180*angle_from_kremlin), bearing.xy = bearing.x*bearing.y)
  

```


#### General price level of Sub Areas
```{r}
  # average price per raion
  train <- train %>% 
    group_by(sub_area) %>% 
    summarize(mean_price_raion = mean(price_doc)) %>% 
    mutate(price_rank_raion = rank(mean_price_raion)) %>% 
    right_join(train,by="sub_area")

 test <- train %>% 
    group_by(sub_area) %>% 
    summarize(mean_price_raion = mean(price_doc)) %>% 
    mutate(price_rank_raion = rank(mean_price_raion)) %>% 
    right_join(test,by="sub_area")

  # average price per raion new
  train <- train %>% 
    filter(year >= 2014) %>% 
    group_by(sub_area) %>% 
    summarize(mean_price_raion_new = mean(price_doc)) %>% 
    mutate(price_rank_raion_new = rank(mean_price_raion_new)) %>% 
    right_join(train,by="sub_area")
  
  test <- train %>% 
    filter(year >= 2014) %>% 
    group_by(sub_area) %>% 
    summarize(mean_price_raion_new = mean(price_doc)) %>% 
    mutate(price_rank_raion_new = rank(mean_price_raion_new)) %>%
    right_join(test,by="sub_area")
```

#### Poselenie vs rest
```{r}
train <- train %>% mutate(poselenie = ifelse(str_detect(sub_area, 'Poselenie'),1,0))
test <- test %>% mutate(poselenie = ifelse(str_detect(sub_area, 'Poselenie'),1,0))
```


#### Population characteristics
```{r }
  # population density per raion (i.e. Number of people per square meter)
  train <- train %>% mutate(pop_density_raion = raion_popul/area_m)
  test <- test %>% mutate(pop_density_raion = raion_popul/area_m)
  
  # Demographic structure of the raions
  train <- train %>% mutate(young_proportion = young_all/full_all) # proportion of people younger than working age
  test <- test %>% mutate(young_proportion = young_all/full_all) # proportion of people younger than working age  
  train <- train %>% mutate(work_proportion = work_all/full_all) # proportion of people in working age
  test <- test %>% mutate(work_proportion = work_all/full_all) # proportion of people in working age  
  train <- train %>% mutate(retire_proportion = ekder_all/full_all) # proportion of people older than working age
  test <- test %>% mutate(retire_proportion = ekder_all/full_all) # proportion of people older than working age  

```

#### Building information
```{r }
  # average building height per raion
  train <- full %>% 
    group_by(sub_area) %>% 
    summarize(mean_building_height = mean(max_floor,na.rm=T)) %>% 
    right_join(train,by="sub_area")
  test <- full %>% 
    group_by(sub_area) %>% 
    summarize(mean_building_height = mean(max_floor,na.rm=T)) %>% 
    right_join(test,by="sub_area")

  # Proportion of houses with certain build materials (e.g. 10% build_count_wood)
  train<-train %>%  mutate_each(funs(pct = (.)/raion_build_count_with_builddate_info),matches('^build_count_[a-zA-Z]*$'))
  test<-test %>%  mutate_each(funs(pct = (.)/raion_build_count_with_builddate_info),matches('^build_count_[a-zA-Z]*$'))
  
```

#### Educational characteristics
```{r }
  # ratio of number of pupils and preschool seats
  train <- train %>% mutate(ratio_preschool = children_preschool / preschool_quota)
  test <- test %>% mutate(ratio_preschool = children_preschool / preschool_quota)

  # ratio of number of pupils and school seats
  train <- train %>% mutate(ratio_school = children_school / school_quota)
  test <- test %>% mutate(ratio_school = children_school / school_quota)  

```


### dataset related features
```{r}
  # number of missing values per row (this is going to take a while)
  train <- train %>% mutate(count_na_perrow = apply(., 1, function(x) sum(is.na(x))))
  test <- test %>% mutate(count_na_perrow = apply(., 1, function(x) sum(is.na(x))))
```



#### cleaning
```{r}
train <- train %>% mutate(price_persqm = price_doc/full_sq)

# 4.7 and 6.4
train$full_sq[train$id %in% c(22415,26366)] <- train$full_sq[train$id %in% c(22415,26366)]*10

# 5326 and 394
train$full_sq[train$id %in% c(3530,1613)] <- train$full_sq[train$id %in% c(3530,1613)] / 100

train$full_sq2<-NA
### full_sq <= 4
errors <- train %>% filter(full_sq <= 4)
for (i in 1:nrow(errors)) {
  tmp <- train %>% filter(appartment_name == errors$appartment_name[i], full_sq>10, year==errors$year[i])
  if (nrow(tmp)>=10) {
    tmp_ppsqm <- mean(tmp$price_doc/tmp$full_sq)
  } else {
  tmp <- train %>% filter(appartment_name == errors$appartment_name[i], full_sq>10)
    tmp_ppsqm <- mean(tmp$price_doc/tmp$full_sq)
  }
  errors$full_sq[i] <- round(errors$price_doc[i]/tmp_ppsqm)
}
train$full_sq2[match(errors$id,train$id)]<-errors$full_sq

### achtung. 16746
errors <- train %>% filter(full_sq >= 200, product_type=="OwnerOccupier", n>=5)
for (i in 1:nrow(errors)) {
  tmp <- train %>% filter(appartment_name == errors$appartment_name[i], full_sq<200, year==errors$year[i])
  if (nrow(tmp)>=10) {
    tmp_ppsqm <- mean(tmp$price_doc/tmp$full_sq)
  } else {
  tmp <- train %>% filter(appartment_name == errors$appartment_name[i], full_sq<200)
    tmp_ppsqm <- mean(tmp$price_doc/tmp$full_sq)
  }
  errors$full_sq[i] <- round(errors$price_doc[i]/tmp_ppsqm)
}
train$full_sq2[match(errors$id,train$id)]<-errors$full_sq



arrange(train,desc(price_persqm)) %>% select(id,price_persqm, price_doc, full_sq, product_type, year, everything()) %>% View()

train$price_doc[train$id == 20391] <- train$price_doc[train$id == 20391] + 11000000
train$price_doc[train$id == 30276] <- train$price_doc[train$id == 30276]*10
train$price_doc[train$id == 635] <- train$price_doc[train$id == 635]*10

# usd statt euro
train$price_doc[train$id == 1264] <- 11160000


train <- train %>% mutate(price_persqm = price_doc/full_sq)

arrange(train,price_persqm) %>% select(id,price_persqm, price_doc, full_sq, product_type, year, everything()) %>% View()

arrange(train,desc(product_type),price_persqm) %>% select(id,price_persqm, price_doc, full_sq, product_type, year, everything()) %>% View()

train %>% filter(appartment_name=='Obruchevskoe 2.07060') %>%  select(id,price_persqm, price_doc, full_sq, product_type, year, everything())%>% View()

```

#### Fix missing product_type in test set

```{r}

test <- test %>% mutate(product_type=as.character(product_type))

test <- test %>% mutate(product_type = ifelse(is.na(product_type) & build_year>2016,"OwnerOccupier",product_type)) # OwnerOccupier

test <- test %>% mutate(product_type = ifelse(is.na(product_type),"Investment",product_type)) # Investment

test <- test %>% mutate(product_type = as.factor(product_type))

```

## macro

```{r}
macro <- macro %>% mutate(quarter = str_c(year(timestamp),quarter(timestamp),sep="_"))
tmp1 <- macro %>% group_by(quarter) %>% summarize(m1=mean(cpi)) %>% mutate(m2=lag(m1), change_cpi=(m1-m2)/m2)

tmp2 <- train %>% filter(product_type=="OwnerOccupier") %>% group_by(quarter) %>% summarize(m1=mean(price_doc)) %>% mutate(m2=lag(m1), change_price=(m1-m2)/m2)

tmp2 %>% left_join(tmp1, by="quarter") %>% mutate(change = change_price-change_cpi) %>% View()

```



## undersample strange prices

```{r}
re_investment = 
  train %>% 
  filter(product_type=='Investment',timestamp>='2011-10-01') %>% 
  group_by(ts=substring(timestamp,1,7)) %>% 
  summarise(n=n(),
            n1M=sum(ifelse(price_doc<=1000000,1,0))/n(),
            n2M=sum(ifelse(price_doc==2000000,1,0))/n(),
            n3M=sum(ifelse(price_doc==3000000,1,0))/n())

m1=floor(mean(re_investment$n1M[re_investment$ts>='2015-01'])/10*nrow(train)) #undersampling by magic numbers
m2=floor(mean(re_investment$n2M[re_investment$ts>='2015-01'])/3*nrow(train)) #undersampling by magic numbers
m3=floor(mean(re_investment$n3M[re_investment$ts>='2015-01'])/2*nrow(train)) 

set.seed(1)
i1 = train %>% filter(price_doc<=1000000,product_type=='Investment') %>% sample_n(m1)
i2 = train %>% filter(price_doc==2000000,product_type=='Investment') %>% sample_n(m2)
i3 = train %>% filter(price_doc==3000000,product_type=='Investment') %>% sample_n(m3)

train = train %>% filter(!(price_doc<=1000000 & product_type=='Investment'))
train = train %>% filter(!(price_doc==2000000 & product_type=='Investment'))
train = train %>% filter(!(price_doc==3000000 & product_type=='Investment'))

train = rbind(train,i1,i2,i3) %>% arrange(id)
```

## normalize price_doc

```{r}

mean_prices <- train %>% group_by(year_month,product_type) %>% summarize(mean_prices=mean(price_doc))

train <- train %>% left_join(mean_prices, by=c("year_month","product_type"))

train <- train %>% filter(between(year,2013,2014)) %>% group_by(product_type) %>%  summarize(overall_mean=mean(price_doc)) %>% right_join(train,by="product_type")

train <- train %>% mutate(price_normal = price_doc-mean_prices+overall_mean)

train %>%  ggplot(aes(x=price_doc, group=factor(year),color=factor(year)))+geom_density()+coord_cartesian(xlim=c(0,2e07))+facet_grid(product_type~.)

train %>%  ggplot(aes(x=price_normal,group=factor(year),color=factor(year)))+geom_density()+coord_cartesian(xlim=c(0,2e07))+facet_grid(product_type~.)



train %>%  ggplot(aes(x=log(price_doc+1), group=factor(year),color=factor(year)))+geom_density()+coord_cartesian(xlim=c(14,17.5))+facet_grid(product_type~.)

train %>%  ggplot(aes(x=log(price_normal+1),group=factor(year),color=factor(year)))+geom_density()+coord_cartesian(xlim=c(14,17.5))+facet_grid(product_type~.)

```




### Feature Importance
#### Features
```{r}
outcomes <- train %>% filter(strange_price == 0 & price_normal>0) %>% select(price_normal) %>% .[[1]]
#outcomes <- train %>% select(price_doc) %>% .[[1]]

basic_features <- c("full_sq", "life_sq", "kitch_sq", "num_room", "floor", "max_floor", "material", "build_year", "state", "product_type")

#basic_features <- setdiff(names(train),c("id","timestamp","year","year_month","appartment_name","mean_price_persqm_raion","mean_price_raion_year","mean_price_raion","price_rank_raion","sub_area","price_doc"))

new_features <- c("month_of_year","week_of_year", "day_of_month", "day_of_week", "floor_from_top", "floor_by_maxfloor", "roomsize", "life_proportion", "kitchen_proportion", "extra_area", "age_at_sale", "n_sales_permonth", "distance_from_kremlin", "young_proportion", "work_proportion", "retire_proportion", "mean_building_height", "ratio_preschool",
"ratio_school", "count_na_perrow", "angle_from_kremlin", "bearing.x", "bearing.y", "bearing.xy", "pop_density_raion", "school_education_centers_raion_pct", "hospital_beds_raion_pct", "healthcare_centers_raion_pct", "sport_objects_raion_pct", "additional_education_raion_pct", "shopping_centers_raion_pct", "okrug")

exclude_features <- c("price_normal","mean_prices", "count_na_perrow", "train_test", "price_doc", "timestamp", "id", "mean_price_raion_year", "mean_price_raion", "mean_price_raion_new", "mean_price_persqm_raion", "year", "year_month", "sub_area", "appartment_name", "n", "strange_price","overall_mean")

```


## Importance Analysis
```{r, echo=FALSE, message=FALSE, warning=FALSE}
  #predictors <- c(basic_features,new_features)
  #predictors <- basic_features
  predictors <- setdiff(names(train), exclude_features)

  train_set <- train %>% filter(price_normal>0) %>% select(one_of(predictors))
#  train_set <- train %>% select(one_of(predictors))
  
  test_set <- test %>% select(one_of(predictors))

  dummy <- dummyVars(~.,train_set)
  train_matrix <- predict(dummy,train_set)
  test_matrix <- predict(dummy,test_set)

  train_sparse <- Matrix(train_matrix,sparse = T)
  test_sparse <- Matrix(test_matrix, sparse=T)
  
  dtrain <- xgb.DMatrix(data = train_sparse,label=log(outcomes+1))
  dtest <- xgb.DMatrix(data = test_sparse)  

  #### xgboost params
  param <- list(objective="reg:linear",
              eval_metric = "rmse",
              eta = .2,
              max_depth = 4,
              gamma = 6,
              subsample = .7,
              colsample_bytree = .7,
              min_child_weight=4
  )

  # CV for number of rounds
  xgb_cv <- xgb.cv(data = dtrain,
                  nfold = 5,
                  params = param,
                  nrounds = 150000,
                  maximize = FALSE,
                  prediction = TRUE,
                  early.stop.round = 50,
                  print_every_n = 50,
                  verbose = 1
  )
  rounds <- xgb_cv$best_iteration  
  #rounds<-1000
  
  # Train model
  xgb_model <- xgb.train(data = dtrain,
                       params = param,
                       watchlist = list(train = dtrain),
                       nrounds = rounds,
                       verbose = 0
  )

  imp_matrix_all <- xgb.importance(colnames(train_sparse),xgb_model)

```

We can see that our work payed off. There are several new features having higher importance than the basic features. 
What we also see is that the time features (e.g., day of week) don't seem too important. 

```{r, fig.height=10, width=10, echo=FALSE}
  imp_matrix_all <- imp_matrix_all %>% mutate(group = ifelse(Feature %in% new_features,"new","old"))

  ggplot(head(imp_matrix_all,50),aes(x=reorder(Feature,Gain),y=Gain, fill=group))+geom_bar(stat="identity")+coord_flip(ylim=c(0,0.2))+theme_bw()+labs(x="")
```

### make prediction

```{r}
preds <- data.frame(id=test_id, price_doc = exp(predict(xgb_model,dtest))-1, pt=test_set$product_type)

#preds$price_doc <- preds$price_doc / (mean(preds$price_doc)/7110466)
#preds$price_doc <- preds$price_doc * (6600466/mean(train$price_normal))

preds$price_doc[preds$pt=="Investment"]<-preds$price_doc[preds$pt=="Investment"]/1.1

preds$pt<-NULL
write.csv(preds, '../submission.csv', row.names = FALSE, quote = FALSE)
```

### predict product_type in test set

```{r}

predictors <- c(setdiff(names(train), exclude_features),"id")
train_set <- train %>% filter(strange_price == 0) %>% select(one_of(predictors))
test_set <- test %>% select(one_of(predictors))

## train set = test set
train_set <- test_set %>% filter(!is.na(product_type))
outcomes <- as.numeric(train_set$product_type)-1
train_set <- train_set %>% select(-product_type)

test_set <- test_set %>% filter(is.na(product_type)) %>% select(-product_type)

train_ids <- train_set$id
test_ids <- test_set$id

train_set <- train_set %>% select(-id)
test_set <- test_set %>% select(-id)

train_set <- train_set %>% mutate_if(is.character, as.factor)
test_set <- test_set %>% mutate_if(is.character,as.factor)
train_set$railroad_1line <- NULL
test_set$railroad_1line <- NULL

dummy <- dummyVars(~.,train_set)
train_matrix <- predict(dummy, train_set)
train_sparse <- Matrix(train_matrix,sparse=TRUE)
test_matrix <- predict(dummy, test_set)
test_sparse <- Matrix(test_matrix,sparse=TRUE)

dtrain <- xgb.DMatrix(data = train_sparse,label=outcomes)
dtest <- xgb.DMatrix(data = test_sparse)

  #### xgboost params
  param <- list(objective="binary:logistic",
              eval_metric = "auc",
              eta = .05,
              gamma = 5,
              max_depth = 5,
              subsample = 0.7,
              colsample_bytree = .7
  )

  # CV for number of rounds
  xgb_cv <- xgb.cv(data = dtrain,
                  nfold = 5,
                  params = param,
                  nrounds = 150000,
                  maximize = TRUE,
                  prediction = TRUE,
                  early.stop.round = 50,
                  print_every_n = 10,
                  verbose = 1
  )
  rounds <- xgb_cv$best_iteration  
  
  # Train model
  xgb_model <- xgb.train(data = dtrain,
                       params = param,
                       watchlist = list(train = dtrain),
                       nrounds = rounds,
                       verbose = 1
  )

  predict(xgb_model,dtest)
  
    imp_matrix_all <- xgb.importance(colnames(train_sparse),xgb_model)
ggplot(head(imp_matrix_all,20),aes(x=reorder(Feature,Gain),y=Gain))+geom_bar(stat="identity")+coord_flip(ylim=c(0,0.2))+theme_bw()+labs(x="")
```



### EDA
cafe count
```{r}
tmp <- train %>% select(one_of(c("price_doc", "cafe_count_500", "cafe_count_1000", "cafe_count_1500", "cafe_count_2000", "cafe_count_3000", "cafe_count_5000")))

corrplot(cor(tmp,use = "pairwise.complete.obs"))
```

```{r}
tmp <- train %>% select(c(starts_with('cafe_sum'),one_of("price_doc")))

corrplot(cor(tmp,use = "pairwise.complete.obs"))
```

```{r}
tmp <- train %>% select(c(starts_with('cafe_avg'),one_of("price_doc")))

corrplot(cor(tmp,use = "pairwise.complete.obs"))
```

```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('_price_')))

corrplot(cor(tmp,use = "pairwise.complete.obs"))
```

Der beste Indikator == cafe_count_x_price_1500


```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('church')))

corrplot(cor(tmp,use = "pairwise.complete.obs"))
```

Der beste Indikator == cafe_count_x_price_1500

Tendenziell immer innerhalb 5000 am besten
sport, mosque, leisure, market, prom_part, office_count, office_sqm, trc_count
```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('sport')))
corrplot(cor(tmp,use = "pairwise.complete.obs"))
sort(cor(tmp,use = "pairwise.complete.obs")[1,],decreasing = T)
```

```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('mosque')))
corrplot(cor(tmp,use = "pairwise.complete.obs"))
sort(cor(tmp,use = "pairwise.complete.obs")[1,],decreasing = T)
```

```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('leisure')))
corrplot(cor(tmp,use = "pairwise.complete.obs"))
sort(cor(tmp,use = "pairwise.complete.obs")[1,],decreasing = T)
```

```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('market')))
corrplot(cor(tmp,use = "pairwise.complete.obs"))
sort(cor(tmp,use = "pairwise.complete.obs")[1,],decreasing = T)
```

```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('prom_part')))
corrplot(cor(tmp,use = "pairwise.complete.obs"))
sort(cor(tmp,use = "pairwise.complete.obs")[1,],decreasing = T)
```

```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('green_part')))
corrplot(cor(tmp,use = "pairwise.complete.obs"))
sort(cor(tmp,use = "pairwise.complete.obs")[1,])
```

```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('office_count')))
corrplot(cor(tmp,use = "pairwise.complete.obs"))
sort(cor(tmp,use = "pairwise.complete.obs")[1,],decreasing = T)
```

```{r}
tmp <- train %>% filter(year>=2014) %>% select(c(one_of("price_doc"),contains('trc_count')))
corrplot(cor(tmp,use = "pairwise.complete.obs"))
sort(cor(tmp,use = "pairwise.complete.obs")[1,],decreasing = T)
```